---
title: "Food Waste"
author: "Nuno Fernandes"
output: github_document
---
## Preprocessing

### read.csv
```{r}
setwd("~/2021/food waste")
food<-read.csv("Comportamento_Alimentar.csv")
```

### packages
```{r, results="hide",  warning=FALSE, message=FALSE}
packages <- c("glmm", "lmerTest", "lme4", "Hmisc", "lattice", "ggplot2", "sjPlot")

installed_packages <- packages %in% row.names(installed.packages())
if (any(installed_packages == FALSE)) {
  install.packages(packages[!installed.packages])
}

lapply(packages, library, character.only = TRUE)
``` 

### coding dimension
````{r}

food$Dimension[food$Dimension==1]<-"aStatus"
food$Dimension[food$Dimension==2]<-"Environment"
food$Dimension[food$Dimension==3]<-"Economic"
food$Dimension[food$Dimension==4]<-"Social"
```

### coding temporal framing
```{r}
food$Tem_Val[food$Tem_Val==0]<-"P+F-"
food$Tem_Val[food$Tem_Val==1]<-"P-F+"
```

### coding dv:food choices
```{r}
food$escolha[food$escolha==0]<-"excess"
food$escolha[food$escolha==1]<-"enough"
```

### as.factor
```{r}
food$id<-food$ï..id 
food$id<-as.factor(food$id)
food$Scenario<-as.factor(food$Scenario)
food$Dimension<-as.factor(food$Dimension)
food$Tem_Val<-as.factor(food$Tem_Val)
food$escolha<-as.factor(food$escolha)
``` 

## Statistical Analysis
```{r, message=FALSE}
m1<- glmer(escolha ~ Dimension*Tem_Val + Q_comida_fora + (1|id/Scenario),
           data = food, family = binomial, control = glmerControl(optimizer = "bobyqa"))

m2<- glmer(escolha ~ Dimension*Q_consumo_sustentavel +  Q_comida_fora + (1|id/Scenario),
           data = food, family = binomial, control = glmerControl(optimizer = "bobyqa"))
``` 


### summary m1
```{r, message=FALSE}
summary(m1)
anova(m1)
``` 
### Confidence Intervals m1
```{r}
confint(m1, method = "Wald")
```
### table m1 - escolha ~ Dimension * Tem_Val + Q_comida_fora + (1 | id/Scenario)
```{r}
tab_model(m1)
```

### summary m2
```{r, message=FALSE}
summary(m2)
anova(m2)
``` 

### Confidence Intervals m2
```{r}
confint(m2, method = "Wald")
```

### table m2 - escolha ~ Dimension*Q_consumo_sustentavel +  Q_comida_fora + (1|id/Scenario)
```{r}
tab_model(m2)
```

## Data Visualization

### Probability of cooking just enough food (violin plot)
```{r, warning=FALSE, message=FALSE,dev=c('png', 'tiff')}
food<-read.csv("Comportamento_Alimentar.csv")
food$Dimension[food$Dimension==1]<-"Status"
food$Dimension[food$Dimension==2]<-"Environmental"
food$Dimension[food$Dimension==3]<-"Economic"
food$Dimension[food$Dimension==4]<-"Social"

ggplot(data = food, aes(x = Dimension, y = PredictedProbability_01)) +
  ylab("Probability of choosing to cook just enough food") + xlab("Dimension") +
  theme(axis.title.x = element_text(color="black", size = 15),
        axis.title.y = element_text(color="black", size = 15),
        axis.text.x = element_text(size = 13),
        axis.text.y = element_text(size = 13)) +
  scale_x_discrete(name ="Dimension", 
                   limits=c("Status","Environmental","Economic","Social")) +
  ylim(0.00, 1.00) +
  geom_violin(scale = "area", adjust = .8) +
  stat_summary(fun.data=mean_sdl, fun.args = list(mult = .5), 
               geom="errorbar", color="red", width = .1) +
  stat_summary(fun.y=mean, geom="point", color="red") +
  geom_smooth(method = "glmer") 

``` 
  
### Probability of cooking just enough food (jitter) - https://doi.org/10.1002/bdm.2274
```{r, dev=c('png', 'tiff'), warning=FALSE}
apatheme <- theme_bw(base_size = 12)+
  theme(panel.grid.major=element_blank(),
        panel.grid.minor=element_blank())

fixd.plot <- ggplot(food, aes(x = Dimension, y = PredictedProbability_01))  +
  geom_point(position = position_jitter(width = .1), alpha = .2) +
  # geom_point(size = 1, colour = "grey60", alpha = .5, position = position_jitter(width = .3, height = 0)) +
  #geom_errorbar(data = food, aes(x = diff, y = m, ymin = m -sd, ymax = m + sd), 
                #position = position_nudge(x = -.2), width = .2) +
scale_x_discrete(name ="Dimension", 
                   limits=c("Status","Environmental","Economic","Social")) +
  
  #confirm if this is to remove or not
  #geom_point(data = food, aes(y = PredictedProbability_01), size = 4, position = position_nudge(x = -.2))  + 
  #error bar
  stat_summary(fun.data=mean_sdl, fun.args = list(mult = .5), 
               geom="errorbar", color="red", width = .1) + 
  stat_summary(fun=mean, geom="point", color="red") +
  
    ylab("Probability of cooking just enough food") + xlab("Dimension") + apatheme
ggsave("figure4.pdf", width=4, height=4, unit='in', dpi=300)

fixd.plot
```
