---
title: "Food Waste"
author: "Nuno Fernandes"
output: github_document
---
## Preprocessing

### read.csv
```{r}
#setwd("~/2021/food waste")
food<-read.csv("Comportamento_Alimentar.csv")
```

### packages
```{r, results="hide",  warning=FALSE, message=FALSE}
packages <- c("glmm", "lmerTest", "lme4", "Hmisc", "lattice", "ggplot2", "sjPlot", "effects", "plyr","emmeans","dplyr")

installed_packages <- packages %in% row.names(installed.packages())
if (any(installed_packages == FALSE)) {
  install.packages(packages[!installed.packages])
}

lapply(packages, library, character.only = TRUE)
``` 

### coding dimension
````{r}

food$Dimension[food$Dimension==1]<-"aStatus"
food$Dimension[food$Dimension==2]<-"Environment"
food$Dimension[food$Dimension==3]<-"Economic"
food$Dimension[food$Dimension==4]<-"Social"
```

### coding temporal framing
```{r}
food$Tem_Val[food$Tem_Val==0]<-"P+F-"
food$Tem_Val[food$Tem_Val==1]<-"P-F+"
```

### coding dv:food choices
```{r}
food$escolha[food$escolha==0]<-"extra"
food$escolha[food$escolha==1]<-"enough"
```

### as.factor
```{r}
#food$id<-food$ï..id 
food$id<-as.factor(food$id)
food$Scenario<-as.factor(food$Scenario)
food$Dimension<-as.factor(food$Dimension)
food$Tem_Val<-as.factor(food$Tem_Val)
food$escolha<-as.factor(food$escolha)
``` 

## Statistical Analysis
```{r, message=FALSE}
m1<- glmer(escolha ~ Dimension*Tem_Val + Q_comida_fora + Dimension + (1|id/Scenario),
           data = food, family = binomial, control = glmerControl(optimizer = "bobyqa"))

m2<- glmer(escolha ~ Dimension*Q_consumo_sustentavel +  Q_comida_fora + (1|id/Scenario),
           data = food, family = binomial, control = glmerControl(optimizer = "bobyqa"))
``` 
### summary m1
```{r, message=FALSE}
summary(m1)
anova(m1)
``` 
### Confidence Intervals m1
```{r}
confint(m1, method = "Wald")
```
### table m1 - escolha ~ Dimension * Tem_Val + Q_comida_fora + (1 | id/Scenario)
```{r}
tab_model(m1)
```

### summary m2
```{r, message=FALSE}
summary(m2)
anova(m2)
``` 

### Confidence Intervals m2
```{r}
confint(m2, method = "Wald")
```

### table m2 - escolha ~ Dimension*Q_consumo_sustentavel +  Q_comida_fora + (1|id/Scenario)
```{r}
tab_model(m2)
```


```{r}
#emm <- emmeans(m1, ~ Tem_Val * Dimension)

emmean <- ref_grid(m1)
#emmean <- emmeans(pigs.rg, c("Tem_Val","Dimension"))
#test(pigs.emm.s)
#test(pigs.emm.s, by = "Dimension")
#pairs(pigs.emm.s)
emmean
```

```{r}
warp.pw <- pairs(emmeans(m1, ~ Dimension|Tem_Val))
warp.pw
```

```{r}
confint(warp.pw)
```
```{r}
#apa
theme_apa <- function(base_size = 12, base_family = "", box = FALSE) {
  adapted_theme <- ggplot2::theme_bw(base_size, base_family) +
    ggplot2::theme(
      plot.title = ggplot2::element_text(size = ggplot2::rel(1.1), margin = ggplot2::margin(0, 0, ggplot2::rel(14), 0), hjust = 0.5)
      , plot.subtitle = ggplot2::element_text(size = ggplot2::rel(0.8), margin = ggplot2::margin(ggplot2::rel(-7), 0, ggplot2::rel(14), 0), hjust = 0.5)

      # , axis.title = ggplot2::element_text(size = ggplot2::rel(1.1))
      , axis.title.x = ggplot2::element_text(size = ggplot2::rel(1), lineheight = ggplot2::rel(1.1), margin = ggplot2::margin(ggplot2::rel(12), 0, 0, 0))
      , axis.title.x.top = ggplot2::element_text(size = ggplot2::rel(1), lineheight = ggplot2::rel(1.1), margin = ggplot2::margin(0, 0, ggplot2::rel(12), 0))
      , axis.title.y = ggplot2::element_text(size = ggplot2::rel(1), lineheight = ggplot2::rel(1.1), margin = ggplot2::margin(0, ggplot2::rel(12), 0, 0))
      , axis.title.y.right = ggplot2::element_text(size = ggplot2::rel(1), lineheight = ggplot2::rel(1.1), margin = ggplot2::margin(0, 0, 0, ggplot2::rel(12)))
      , axis.ticks.length = ggplot2::unit(ggplot2::rel(6), "points")
      , axis.text = ggplot2::element_text(size = ggplot2::rel(0.9))
      , axis.text.x = ggplot2::element_text(size = ggplot2::rel(1), margin = ggplot2::margin(ggplot2::rel(6), 0, 0, 0))
      , axis.text.y = ggplot2::element_text(size = ggplot2::rel(1), margin = ggplot2::margin(0, ggplot2::rel(6), 0, 0))
      , axis.text.y.right = ggplot2::element_text(size = ggplot2::rel(1), margin = ggplot2::margin(0, 0, 0, ggplot2::rel(6)))
      , axis.line = ggplot2::element_line()
      # , axis.line.x = ggplot2::element_line()
      # , axis.line.y = ggplot2::element_line()

      , legend.title = ggplot2::element_text()
      , legend.key = ggplot2::element_rect(fill = NA, color = NA)
      , legend.key.width = ggplot2::unit(ggplot2::rel(20), "points")
      , legend.key.height = ggplot2::unit(ggplot2::rel(20), "points")
      , legend.margin = ggplot2::margin(
        t = ggplot2::rel(16)
        , r = ggplot2::rel(16)
        , b = ggplot2::rel(16)
        , l = ggplot2::rel(16)
        , unit = "points"
      )

      , panel.spacing = ggplot2::unit(ggplot2::rel(14), "points")
      , panel.grid.major.x = ggplot2::element_blank()
      , panel.grid.minor.x = ggplot2::element_blank()
      , panel.grid.major.y = ggplot2::element_blank()
      , panel.grid.minor.y = ggplot2::element_blank()

      , strip.background = ggplot2::element_rect(fill = NA, color = NA)
      , strip.text.x = ggplot2::element_text(size = ggplot2::rel(1.2), margin = ggplot2::margin(0, 0, ggplot2::rel(10), 0))
      , strip.text.y = ggplot2::element_text(size = ggplot2::rel(1.2), margin = ggplot2::margin(0, 0, 0, ggplot2::rel(10)))
    )

  if(box) {
    adapted_theme <- adapted_theme + ggplot2::theme(panel.border = ggplot2::element_rect(color = "black"))
  } else {
    adapted_theme <- adapted_theme + ggplot2::theme(panel.border = ggplot2::element_blank())
  }

  adapted_theme
}
```

### Interaction plot
```{r}
#preprocess estimates
df1 <- as.data.frame(emmean)

#change labels
revalue(df1$Tem_Val, c("P-F+" = "Immediate losses", "P+F-" = "Future losses")) -> df1$Tem_Val
revalue(df1$Dimension, c("aStatus" = "Status", "Environment" = "Environmental")) -> df1$Dimension
df1 %>% mutate(lower = df1$prediction-df1$SE, higher = df1$prediction + df1$SE) -> df1

#legend
legend <- "Temporal Framing"

apatheme <- theme_bw(base_size = 12)+
  theme(panel.grid.major=element_blank(),
        panel.grid.minor=element_blank())

int_plot <- ggplot(df1, aes(x = factor(Dimension), y = prediction))  +
  
scale_x_discrete(name ="Dimension", 
                   limits=c("Status","Economic","Environmental","Social")) +

  
  geom_errorbar(data=df1,aes(x=Dimension, ymin=lower, ymax=higher, color = Tem_Val), position = position_dodge((0.4)), width = 0.2)+
  
    #shape
  scale_shape_manual(values=c(21,24)) + 
  
     scale_fill_manual(values=c("white","black"))+
  
geom_point(aes(color = Tem_Val, shape = Tem_Val), size = 3, position = position_dodge(0.4))+
  
   geom_line(aes(group = Tem_Val, color = Tem_Val), size = 0.3, position = position_dodge(0.4)) +
  
  #colour
  scale_color_manual(values = c("grey80", "grey30"), legend)+
  
  #shape
  scale_shape_manual(legend, values=c(17,15))+

    ylab("Odds Ratio of Cooking Just Enough") + xlab("Dimension") +
  #apatheme
  theme_apa()

int_plot
```
```{r}
#had some error while rendering, so manually created dataframe below
#emmean <- ref_grid(m1)
#emmean <- emmeans(pigs.rg, c("Dimension"))
#emmean
```
```{r}
df <- data.frame (Dimension  = c("aStatus", "Economic", "Environment", "Social"),
                  emmean = c(1.92, 2.30, 2.35, 2.35),
                  SE = c(0.295,0.300,0.296,0.304))
```

### Dimension main effect
```{r}

#preprocess estimates
#df <- as.data.frame(emmean)
df$mean = df$emmean
df %>% mutate(lower = mean-SE, higher = mean + SE) -> df

#change labels
#revalue(df1$Tem_Val, c("P-F+" = "Immediate losses", "P+F-" = "Future losses")) -> df1$Tem_Val
revalue(df$Dimension, c("aStatus" = "Status", "Environment" = "Environmental")) -> df$Dimension


#legend

apatheme <- theme_bw(base_size = 12)+
  theme(panel.grid.major=element_blank(),
        panel.grid.minor=element_blank())

int_plot <- ggplot(df, aes(x = factor(Dimension), y = mean, group = 1))  +
  
scale_x_discrete(name ="Dimension", 
                   limits=c("Status","Economic","Environmental","Social")) +

  
  
  geom_errorbar(data=df,aes(x=Dimension, ymin=lower, ymax=higher), width=0.2)+
  
  
    #shape
 # scale_shape_manual(values=c(21,24)) + 
  
 #    scale_fill_manual(values=c("white","black"))+
  
geom_point(size = 3, position = position_dodge(0.4))+ #scale_color_manual(values = c("#00AFBB", "#E7B800"))+
  geom_line()+ 
  
    annotate("text", x = 1.5, y = 2.3, label = "*p<.05") +
  

    ylab("Odds Ratio of Cooking Just Enough") + xlab("Dimension") +
  
  #apatheme
  theme_apa()
#ggsave("figure4.pdf", width=4, height=4, unit='in', dpi=300)

int_plot
```




